%%%%%%%%%%%%%%%%%%%%%%%%
% 1) The EMTG-Config.cmake File
%%%%%%%%%%%%%%%%%%%%%%%%

Follow the following instructions:
\begin{enumerate}
	\item Navigate to the \textbf{\textless EMTG\_root\_dir\textgreater}\textbackslash directory
	\item Copy the `EMTG-Config-template.cmake' file and rename to `EMTG-Config.cmake'
	\item Open `EMTG-Config.cmake' in a text editor \\ \emph{This file is heavily commented with specific instructions. The user must know where they installed CSPICE, Boost, and GSL. If building with SNOPT or IPOPT, the user must also know where those packages were installed.}
	\item Set the CSPICE DIR variable to the full path of the CSPICE root directory.
	\begin{enumerate}
		\item If CSPICE were placed in C:\textbackslash SW\_Installs\textbackslash cspice, then the user would type in the EMTG-Config.cmake file \\
		\begin{verbatim}
			set(CSPICE_DIR C:/SW_Installs/cspice)
			 
		\end{verbatim}
		
		\emph{Note the use of forward slashes in the file path even though the Windows file system uses backslashes.}
	\end{enumerate}
	\item Set the SNOPT\_ROOT\_DIR variable to the full path of the SNOPT root directory.
	\begin{enumerate}
		\item If SNOPT  were placed in C:\textbackslash SW\_Installs\textbackslash SNOPT77, then the user would type in the EMTG-Config.cmake file \\
		\begin{verbatim}
			set(SNOPT_ROOT_DIR C:/SW_Installs/SNOPT77)
			 
		\end{verbatim}
		
		\emph{Note the use of forward slashes in the file path even though the Windows file system uses backslashes.}
	\end{enumerate}
	\item If building with \ac{IPOPT}, set the IPOPT\_ROOT\_DIR variable to the full path of the \ac{IPOPT} installation prefix and confirm the include, library, and binary directory hints.
	\begin{enumerate}
		\item If \ac{IPOPT} were placed in C:\textbackslash SW\_Installs\textbackslash ipopt, then the user would type in the EMTG-Config.cmake file \\
		\begin{verbatim}
			set(IPOPT_ROOT_DIR C:/SW_Installs/ipopt)
			set(IPOPT_INCLUDE_DIR ${IPOPT_ROOT_DIR}/include)
			set(IPOPT_LIBRARY_DIR ${IPOPT_ROOT_DIR}/lib)
			set(IPOPT_BIN_DIR ${IPOPT_ROOT_DIR}/bin)
		\end{verbatim}
		\item When consuming a MinGW-built \ac{IPOPT} binary from an \ac{MSVC} build of EMTG, also set IPOPT\_MINGW\_BIN\_DIR to the directory containing the MinGW runtime DLLs required by \ac{IPOPT}.
	\end{enumerate}
	\item Set the BOOST\_ROOT, BOOST\_INCLUDE\_DIR, and BOOST\_LIBRARY\_DIRS variables.
	\begin{enumerate}
		\item BOOST\_ROOT is the full path to the root directory of Boost.
		\item BOOST\_INCLUDE\_DIR is the full path to the directory that contains the Boost header files. For Boost 1.79.0, this is a subdirectory in the Boost root directory called Boost.
		\item BOOST\_LIBRARY\_DIRS is the full path to the directory that holds the Boost libraries after they are built. For Boost 1.79.0, this is a subdirectory in the Boost root directory called stage\textbackslash lib.
	\end{enumerate}
	If Boost were placed in C:\textbackslash SW\_Installs\textbackslash boost\_1\_79\_0, then the user would type in the EMTG-Config.cmake file 
	\begin{verbatim}
		set(BOOST_ROOT C:/SW_Installs/boost_1_79_0) 
		set(BOOST_INCLUDE_DIR ${BOOST_ROOT}/boost) 
		set(BOOST_LIBRARY_DIRS ${BOOST_ROOT}/stage/lib) 
	\end{verbatim}	
	\emph{Note the use of forward slashes in the file path even though the Windows file system uses backslashes.}
	\item Set the GSL\_PATH variable to the full path to the GSL build directory (where the libraries are located). For example, if GSL were placed in C:\textbackslash SW\_Installs\textbackslash gsl-2.4.0, then the user would type in the EMTG-Config.cmake file 
	\begin{verbatim}
		set(GSL_PATH C:/SW_Installs/gsl-2.4.0/build)
	\end{verbatim}
	\emph{Note the use of forward slashes in the file path even though the Windows file system uses backslashes.}
	\item Save the changes made to the EMTG-Config.cmake file
\end{enumerate}
